submission

### 2024-03-09 submission.Rmd
Added commentary to 1.3

As observed earlier for a $\alpha=0.05$ we basically have guaranteed that the null-hypothesis is rejected correctly only after 2 samples. However, this seems strange and thus one might want to adjust the $\alpha$ value to get a more reasonable sample requirement.

@@

## 2.2 Calculating all p-values
**Task description:**: We now wish to perform the previous test for all of the 3116 genes. For each of the genes, fit a linear model that explains cholesterol as a function of the gene expression and compute the p-value of the test.

@@

```
## 2.4 Benjamini-Hochberg procedure
**Task description:**Identify a set of genes linked to the response (aka discoveries). We want to guarantee that the expected proportion of false discoveries (mistakes) is less than 5%. Explain how you proceed and how many genes you discover.

>>>>

As observed earlier for a $\alpha=0.05$ we basically have guaranteed that the null-hypothesis is rejected correctly only after 2 samples.

The conclusion is that th Wilcoxon test breaks down with so few samples. The Wolcoxon table, which is used to obtain the $\alpha$, does not go below a sample size of 5. And in the case that all the values of one distribution is larger, it gives at most an $\alpha$ of 0.1. \
The other case would be to try and fit the data to a distribution. But with so few datapoints, that would be futile. \
The answer to the question is therefore no, one can not make any conclusions.

@@

## 2.2 Calculating all p-values

**Task description:**: We now wish to perform the previous test for all of the 3116 genes. For each of the genes, fit a linear model that explains cholesterol as a function of the gene expression and compute the p-value of the test.

@@

## 2.4 Benjamini-Hochberg procedure

**Task description:**Identify a set of genes linked to the response (aka discoveries). We want to guarantee that the expected proportion of false discoveries (mistakes) is less than 5%. Explain how you proceed and how many genes you discover.
